---
title: "PricingAnalysis"
author: "Mauricio Campos"
date: "19 de diciembre de 2017"
output:
  #pdf_document: default
  html_document: default
---

```{r, echo = FALSE, message = FALSE}
library(here)
library(tidyverse)
library(MASS)
source(here("R", "cleaning.R"), local = TRUE)
```


## Pricing Model

We want to predict price. The first model considered was: Price ~ availability + neighborhood + room type + minimum nights + number of reviews + reviews per month. This first model presented many problems, including a small $R^2$ value of 0.099. Also, observing the diagnostic plots we can see that this model also posed problems of normality, homogeneity of the variance and some really influential points. 

```{r}
mod1 <- lm(price ~ avail + num_reviews + rpm + nb + room_type + min_nights, data = listings)
par(mfrow = c(2,2))
plot(mod1, which = c(1,2,5))
```

Seeing these plots we can also identify several listings that are clear outliers. These listings had prices above \$1000. It is important to note that in the whole data set only `r sum(listings$price > 1000)`listings have prices above that price range. For exploration purposes, the three influential observations were removed from the model and then fitted again and the results were that minimum nights was no longer a significant variable in the model. 

We considered doing a Box Cox transformation:

```{r}
bc <- boxcox(lm(price ~ avail + num_reviews + rpm + nb + room_type, 
          data = listings), lambda = seq(-0.5,0,by = 0.01))
```

We can see from the confidence interval that we can use the value of $\lambda = -0.4$ to transform price. We then fitted the model again but with the transformed price. Observing the diagnostic plots we can see that the original problems haven been fixed. The $R^2$ was also increased to 0.3139. 

```{r}
listings$price.bc <- listings$price^-0.4
mod2 <- lm(price.bc ~ avail + num_reviews + rpm + nb + room_type + min_nights, data = listings)
par(mfrow = c(2,2))
plot(mod2, which = c(1,2,5))
```

However, in this model minimum nights was no longer a significant variable. We decided to use leaps to select the best model, observing both AIC and BIC. The result was that the best model (with the lowest AIC and BIC) was the following:

Price^-0.4^ ~ availability + neighborhood + room type + number of reviews + reviews per month. 

With the following summary statistics:

```{r}
mod3 <- lm(price.bc ~ avail + num_reviews + rpm + nb + room_type, data = listings)
summary(mod3)
```

Due to the transformation of price most of the interpretability of the coefficients on price is gone, but we can still interpret their effect on the transformed price. We can see, for example, that of all the Neighborhood dummy variables, San Marco has the most negative coefficient, meaning that in average San Marco has the lowest transformed price, if the remaining variables remain constant. Since the transformation on price is inverse then this could translate to a Neighborhood with higher prices in average. For example, Lido has the most positive coefficient, so we would expect it, on average, to have the lowest prices. This can be observed through the following scatterplots. 

```{r scatter_plots, echo = FALSE}
listings <- listings %>% 
  mutate(preds = fitted(mod3)^(-1/0.4))

ggplot(listings, aes(x = rpm, y = preds)) +
  geom_jitter(aes(color = nb), alpha = 0.5) +
  ylab('Predicted Price') +
  xlab('Reviews Per Month') +
  ggthemes::theme_hc()
```