---
title: "Considerations for the Modern Pirate: Venice"
author: "Mauricio Campos, Josh Loyal, Austin Jay Warner"
date: "December 11, 2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(here)

source(here("R", "stop_words.R"))
source(here("R", "cleaning.R"))
source(here("R", "text_model.R"))
#source(here("R", "eda.R"))
source(here("R", "significance.R"))
```





##Investigating Neighborhood Significance on Price
##Data Summary and Preparation

Intuitively, the location of a listing will have a large impact on the pricing in a predictive sense. Our data gives us several ways of measuring the location of a listing: the neighborhood of the listing, the neighborhood group of the listing, the latitude, and the longitude. These covariates are strongly correlated and so we decide to remove some of these predictors. The most interpretable of these covariates are neighborhood and neighborhood group. Since a given neighborhood is either on the island or mainland, it is sufficient to consider neighborhoods. 

Once we have decided to use neighborhoods as our geographical predictor, we face the challenge of scale. The neighborhood predictor, as a categorical variable, has 56 levels, which is simply too many levels for the classical techniques that we have studied throughout the semester in STAT425. 

We decided to reduce the number of neighborhoods in our analysis. The neighborhoods with the most listings are, "San Marco", "Castello", "Cannaregio", "Dorsoduro", "Giudecca", "Lido", "Santa Croce", "Murano", and "San Polo." These nine neighborhoods account for 81.5% of listings. We therefore re-coded the neighborhood factor levels to be these nine neighborhoods. We also think that these neighborhood are the most convenient for pirates: each of these neighborhoods is accessible by water. 

##Analysis

To check for pairwise differences in price between neighborhoods, we implemented Tukey's HSD at an overall significance level of 0.05. 


We found that there are significant differences in pricing between Dorsoduro and Castello, Dorsoduro and Cannaregio, Dorsoduro and Lido, as well as between San Marco and Cannaregio, San Marco and Castello, San Marco and santa Croce, and San Marco and Lido. 

```{r}
(ggplot(sigData, aes(x=namesOne, y=namesTwo, fill=isSign,  col = "black")) + geom_tile(col="black") 
+ scale_fill_manual(values = c("#F1BB7B", "#FD6467"), name="Significant") + labs( x = "Neighborhood", y = "Neighborhood", title = "Significance"))
```

We conclude from this analysis that Dorsoduro and San Marco are priced differently than the other neighborhoods. 

```{r}
(ggplot(listings, aes(x = nb, y = price, color = nb)) +
      geom_boxplot() +
      coord_flip() +
      #scale_color_manual(values=neighborhood_hues()) +
      #scale_color_discrete("") +
      xlab('Venice Neighborhood') +
      ylab('Actual Price Per Night ($)'))
```

In particular, it appears that Dorsoduro and San Marco are priced higher than other neighborhoods. 




##Conclusion

